---
title: "LBI method: Assessing the sensitivity of length-indicator methods for resources in the Atlantic waters"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
  pdf_document:
    number_sections: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Nephrops norvegicus FU25

## Nephrops norvegicus FU25 Males


```{r Table1, warning=FALSE, message=FALSE, echo=FALSE,include=FALSE}
library(kableExtra)
library(tidyverse)

# require (rJava)
# .jinit()
# .jcall('java.lang.System','S','getProperty','java.version')
# [1] "1.8.0_211"
# devtools::install_github('davidgohel/ReporteRsjars')
# devtools::install_github('davidgohel/ReporteRs')
library(LBSPR) 
library(reshape2)
library(ggplot2) 
library(tidyr)
library(ReporteRs) 
source("https://raw.githubusercontent.com/ices-tools-dev/LBIndicator_shiny/master/utilities.R") 
source("utilities_vpaz.R") 
```

Life history parameters:

$L_{mat}$ = 25.0 mm. 
$L_{inf}^{LIT}$ = 86.0 mm. 
${M/k}^{LIT}$ = 1.9. 

Below, catch/landings at length per year and  mean weights-at-length per year are loaded.
  
```{r  message=FALSE, warning=FALSE}

wal <- read.csv("25_Males_w.csv", stringsAsFactors = FALSE)
head(wal)
freq <- read.csv("25_Males.csv",  stringsAsFactors = FALSE)
head(freq)
bin_plot(freq, 1, "mm")

```

On based on the previous plots of the length distribution 
BinWidth is fixed equal to 1.

Reference model:

  
```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 1, "mm", linf = 86.0 , lmat = 25.0 , mk_ratio = 1.90 ,wal)
```

Underestimated ${M/k}^{LIT}$.


```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 1, "mm", linf=86.0, lmat=25.0, mk_ratio=0.75*1.9,wal)
```

Overestimated ${M/k}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 1, "mm", linf=86.0, lmat=25.0, mk_ratio=1.25*1.9,wal)

```

M/k=1.5.
 
```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 1, "m", linf=86.0, lmat=25.0, mk_ratio=1.5,wal)
```

Underestimated $L_{inf}^{LIT}$.


```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 1, "mm", linf=0.75*86.0, lmat=25.0, mk_ratio=1.9,wal)
```


Overestimated $L_{inf}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 1, "mm", linf=1.25*86.0, lmat=25.0, mk_ratio=1.9,wal)
```



## Nephrops norvegicus FU25 Females
Life history parameters:
  
$L_{mat}$ = 28.0 mm. 
$L_{inf}^{LIT}$ = 71.0 mm. 
${M/k}^{LIT}$ = 1.9.


Below, catch/landings at length per year and  mean weights-at-length per year are loaded.
  
```{r  message=FALSE, warning=FALSE}

wal <- read.csv("25_Females_w.csv", stringsAsFactors = FALSE)
freq <- read.csv("25_Females.csv",  stringsAsFactors = FALSE)
head(wal)
head(freq)
bin_plot(freq, 1, "mm")
```

On based on the previous plots of the length distribution 
  BinWidth is fixed equal to 1.
  
Reference model:
  
```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 1, "mm", linf = 71.0 , lmat = 28.0 , mk_ratio = 1.90 ,wal)
```

Underestimated ${M/k}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 1, "mm", linf=71.0, lmat=28.0, mk_ratio=0.75*1.9,wal)
```

Overestimated ${M/k}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 1, "mm", linf=71.0, lmat=28.0, mk_ratio=1.25*1.9,wal)
```

M/k=1.5.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 1, "m", linf=71.0, lmat=28.0, mk_ratio=1.5,wal)
```

Underestimated $L_{inf}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 1, "mm", linf=0.75*71.0, lmat=28.0, mk_ratio=1.9,wal)
```

Overestimated $L_{inf}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 1, "mm", linf=1.25*71.0, lmat=28.0, mk_ratio=1.9,wal)
```


# Nephrops norvegicus FU2627 

## Nephrops norvegicus FU2627 Males 

Life history parameters:
  
  $L_{mat}$ = 28.0 mm. 
  $L_{inf}^{LIT}$ = 80.0 mm. 
  ${M/k}^{LIT}$ = 2. 
  
  Below, catch/landings at length per year and  mean weights-at-length per year are loaded.
  


  
```{r  message=FALSE, warning=FALSE}
wal <- read.csv("FU2627_PesosMales_1988_2019_medio.csv", stringsAsFactors = FALSE)
freq <- read.csv("FU2627_tallasMales_1988_2019.csv", stringsAsFactors = FALSE)
head(freq)
head(wal)
bin_plot(freq, 1, "mm")
bin_plot(freq, 2, "mm")
```

On based on the previous plots of the length distribution 
  BinWidth is fixed equal to 2.


Reference model:
 
 
```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "mm", linf=80, lmat=28, mk_ratio=2,wal)

```

Underestimated ${M/k}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "mm", linf=80, lmat=28, mk_ratio=0.75*2,wal)
```

Overestimated ${M/k}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "mm", linf=80, lmat=28, mk_ratio=1.25*2,wal)
```

M/k=1.5.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "mm", linf=80, lmat=28, mk_ratio=1.5,wal)
```

Underestimated $L_{inf}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "mm", linf=0.75*80, lmat=28, mk_ratio=2,wal)
```

Overestimated $L_{inf}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "mm", linf=1.25*80, lmat=28, mk_ratio=2,wal)
```



## Nephrops norvegicus FU2627 Females

Life history parameters:
  
  $L_{mat}$ = 26.0 mm. 
  $L_{inf}^{LIT}$ = 65.0 mm. 
  ${M/k}^{LIT}$ = 2.5 
  
  Below, catch/landings at length per year and  mean weights-at-length per year are loaded.
  

```{r  message=FALSE, warning=FALSE}
wal <- read.csv("FU2627_PesosFemales_1988_2019_medio.csv", stringsAsFactors = FALSE)
freq <- read.csv("FU2627_tallasFemales_1988_2019.csv", stringsAsFactors = FALSE)
head(freq)
head(wal)
bin_plot(freq, 1, "cm")
bin_plot(freq, 2, "cm")
```
  
  
On based on the previous plots of the length distribution 
BinWidth is fixed equal to 2.

Reference model:

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "mm", linf=65, lmat=26, mk_ratio=2.5,wal)
```

Underestimated ${M/k}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "mm", linf=65, lmat=26, mk_ratio=0.75*2.5,wal)
```

Overestimated ${M/k}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "mm", linf=65, lmat=26, mk_ratio=1.25*2.5,wal)
```

M/k=1.5.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "mm", linf=65, lmat=26, mk_ratio=1.5,wal)
```

Underestimated $L_{inf}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "mm", linf=0.75*65, lmat=26, mk_ratio=2.5,wal)
```

Overestimated $L_{inf}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "mm", linf=1.25*65, lmat=26, mk_ratio=2.5,wal)
```

# Galeus melastomus

Life history parameters:
  
  $L_{mat}$ = 54.2 cm. 
  $L_{inf}^{LIT}$ = 75.0 cm. 
  ${M/k}^{LIT}$ = 1.5. 
  
Below, catch/landings at length per year and  mean weights-at-length per year are loaded.

```{r  message=FALSE, warning=FALSE}
wal <- read.csv("Pin8c9awal.csv",sep=",")
head(wal)
freq <- read.csv("Pin8c9afreq.csv", stringsAsFactors = FALSE)
head(freq)
bin_plot(freq, 1, "cm")
bin_plot(freq, 2, "cm")
```

On based on the previous plots of the length distribution 
BinWidth is fixed equal to 1.
  
Reference model:


```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "cm", linf=75.0, lmat=54.2, mk_ratio=1.5,wal)
```

Underestimated ${M/k}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "cm", linf=75.0, lmat=54.2, mk_ratio=0.75*1.5,wal)
```

Overestimated ${M/k}^{LIT}$

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "cm", linf=75.0, lmat=54.2, mk_ratio=1.25*1.5,wal)
```

Underestimated $L_{inf}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "cm", linf=0.75*75.0, lmat=54.2, mk_ratio=1.5,wal)
```

Overestimated $L_{inf}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "cm", linf=1.25*75.0, lmat=54.2, mk_ratio=1.5,wal)
```

# Engraulis encrasicolus

Life history parameters:
  
  $L_{mat}$ = 11.2 cm
  $L_{inf}^{LIT}$ = 18.95 cm. 
  ${M/k}^{LIT}$ = 1.44.
  
Below, catch/landings at length per year and  mean weights-at-length per year are loaded.


```{r  message=FALSE, warning=FALSE}
MK<-1.44
Linf<-18.95
Lmat<-11.2
wal <- read.csv("wal_anchovy_fv.csv", stringsAsFactors = FALSE)
freq <- read.csv("lengthfreq_anchovy_fv.csv", stringsAsFactors = FALSE)
head(freq)
head(wal)
bin_plot(freq, 1, "cm")
bin_plot(freq, 2, "cm")
```

On based on the previous plots of the length distribution 
  BinWidth is fixed equal to 2.
  
Reference model:  

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "cm", linf=Linf, lmat=Lmat, mk_ratio=MK ,wal)

```

Underestimated ${M/k}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "cm", linf=Linf, lmat=Lmat, mk_ratio=MK*0.75,wal)

```

Overestimated ${M/k}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "cm", linf=Linf, lmat=Lmat, mk_ratio=MK*1.25,wal)

```

 M/k=1.5.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "cm", linf=Linf, lmat=Lmat, mk_ratio=1.5,wal)

```

Underestimated $L_{inf}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "cm", linf=Linf*0.75, lmat=Lmat, mk_ratio=MK,wal)

```

Overestimated $L_{inf}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "cm", linf=Linf*1.25, lmat=Lmat, mk_ratio=MK,wal)


```


# Pollachius pollachius


Life history parameters:
  
  $L_{mat}$ = 42.3 cm. 
  $L_{inf}^{LIT}$ = 98.2 cm. 
  ${M/k}^{LIT}$ = 1.648352. 
  
Below, catch/landings at length per year and  mean weights-at-length per year are loaded.
  

```{r  message=FALSE, warning=FALSE}
freq <- read.csv("Pol89afreq.csv", stringsAsFactors = FALSE)
head(freq)
wal <- read.csv("Pol89awal.csv", stringsAsFactors = FALSE)
head(wal)
bin_plot(freq, 4, "cm")
```

On based on the previous plots of the length distribution 
BinWidth is fixed equal to 4.

Reference model:

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 4, "cm", linf=98.2, lmat=42.3, mk_ratio=1.648352,wal)
```

Underestimated ${M/k}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 4, "cm", linf=98.2, lmat=42.3, mk_ratio=0.75*1.648352,wal)
```

Overestimated ${M/k}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 4, "cm", linf=98.2, lmat=42.3, mk_ratio=1.25*1.648352,wal)
```

M/k=1.5.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 4, "cm", linf=98.2, lmat=42.3, mk_ratio=1.5,wal)
```

Underestimated $L_{inf}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 4, "cm", linf=0.75*98.2, lmat=42.3, mk_ratio=1.648352,wal)
```

Overestimated $L_{inf}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 4, "cm", linf=1.25*98.2, lmat=42.3, mk_ratio=1.648352,wal)
```

# Pagellus bogaraveo

Life history parameters:
  
  $L_{mat}$ = 33 cm. 
  $L_{inf}^{LIT}$ = 62 cm. 
  ${M/k}^{LIT}$ = 1.42. 
  
Below, catch/landings at length per year and  mean weights-at-length per year are loaded.
  


```{r  message=FALSE, warning=FALSE}
wal <- read.csv("SBR9_mw.csv", stringsAsFactors = FALSE)
freq <- read.csv("SBR9_numbers.csv", stringsAsFactors = FALSE)
Linf<-62
Lmat<-33
MK<-1.42

head(freq)
head(wal)
bin_plot(freq, 1, "cm")
bin_plot(freq, 2, "cm")
```

On based on the previous plots of the length distribution 
BinWidth is fixed equal to 1.
  
Reference model:


```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "cm", linf=Linf, lmat=Lmat, mk_ratio=MK ,wal)
```

Underestimated ${M/k}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "cm", linf=Linf, lmat=Lmat, mk_ratio=MK*0.75,wal)
```

Overestimated ${M/k}^{LIT}$.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "cm", linf=Linf, lmat=Lmat, mk_ratio=MK*1.25,wal)
```

M/k=1.5.

```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "cm", linf=Linf, lmat=Lmat, mk_ratio=1.5,wal)
```

Underestimated $L_{inf}^{LIT}$.


```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "cm", linf=Linf*0.75, lmat=Lmat, mk_ratio=MK,wal)
```

Overestimated $L_{inf}^{LIT}$.


```{r  message=FALSE, warning=FALSE}
lb_tableSH(freq, 2, "cm", linf=Linf*1.25, lmat=Lmat, mk_ratio=MK,wal)
```

# Trisopterus luscus

Life history parameters:
  
  $L_{mat}$ = 19.2 cm. 
  $L_{inf}^{LIT}$ = 46.7 cm. 
  ${M/k}^{LIT}$ = 1.761846. 
  
Below, catch/landings at length per year and  mean weights-at-length per year are loaded.
  

```{r message=FALSE, warning=FALSE}

LHTs <- data.frame(t(c("Trisopterus luscus", 19.2, 1, 46.7, 0.21, 1.27, 9)))
colnames(LHTs) <- c("Sp", "L50", "A50", "Linf", "K", "t0", "Amax")

LHTs$MKvbgf <- 1.761846
LHTs$MKnls <- 3.111105
LHTs$MK <- 1.5

library(readr)
faneca <- read_csv("faneca_ieo.csv")
sizeDat <- na.omit(faneca %>%
                    select(TLength, Year))
anho <- as.character(unique(sort(faneca$Year)))
sizeDat <- data.frame(sizeDat)
br = seq(min(sizeDat$TLength), max(sizeDat$TLength) + 1, by = 1)
ranges = paste(head(br, -1), br[-1], sep = " - ")

sizeDat <- unstack(sizeDat)

freq <- data.frame(matrix(NA, nrow = length(br)-1, ncol = length(anho)+1))

for (i in 1:length(anho)) {
  freq[, 1] <- head(br, -1)
  freq[, i + 1] <-
    hist(
      sizeDat[[i]],
      breaks = br - 1,
      include.lowest = TRUE,
      plot = FALSE
    )$counts
  colnames(freq) <- c("MeanLength", anho)
}

freq[,1]=seq(10.5,43.5)
br=seq(10.5,43.5)
head(freq)

alfaWL=0.01303439
betaWL=2.969518

wal <- freq
for (i in 2:dim(freq)[2]) {
  wal[, i] <- alfaWL * ((br) ^ betaWL)
}
colnames(wal) <- c("MeanLength", anho)
head(wal)
bin_plot(freq, 1, "cm")
```

On based on the previous plots of the length distribution 
BinWidth is fixed equal to 1.
  
Reference model:


```{r message=FALSE, warning=FALSE}
lb_tableSH(freq, 1, "cm", 46.7 , 19.2, 1.761846, wal)
```

Underestimated ${M/k}^{LIT}$.


```{r message=FALSE, warning=FALSE}
lb_tableSH(freq, 1,"cm",46.7 , 19.2, 0.75*1.761846, wal)

```

Overestimated ${M/k}^{LIT}$.

```{r message=FALSE, warning=FALSE}
lb_tableSH(freq, 1,"cm",46.7 , 19.2, 1.25*1.761846, wal)

```


M/k=1.5.


```{r message=FALSE, warning=FALSE}
lb_tableSH(freq, 1,"cm",46.7 , 19.2, 1.5, wal)

```

Underestimated $L_{inf}^{LIT}$.


```{r message=FALSE, warning=FALSE}
lb_tableSH(freq, 1,"cm",0.75*46.7 , 19.2, 1.761846, wal)

```

Overestimated $L_{inf}^{LIT}$.


```{r message=FALSE, warning=FALSE}
lb_tableSH(freq, 1,"cm",1.25*46.7 , 19.2, 1.761846, wal)

```
