---
title: "Length Based Spawning Potential Ratio (LB-SPR)"
subtitle: "Aplicación al stock costero de Galicia de Trisopterus luscus"
author: "A. Alonso-Fernández; J. Otero"
date: "Octubre de 2020"
output:
  html_document:
    theme: cerulean
    number_sections: yes
    toc: yes
    toc_float: yes
  pdf_document:
    number_sections: yes
    toc: yes
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction
## What is Spawning Potential ratio (SPR)?
- Spawning Potential ratio (SPR) is defined as the proportion of Spawning Biomass per recruit (SBPR) in an exploited stock with regards to SBPR in an unfished (virgin) stock. 
- The rationale behind is that the abundance at length in the population decreases with ageing (length) because of the mortality (M and F). 
- A virgin population will have a larger amount of large mature individuals than an exploited population. 
- The SPR ranges between 1 (virgin population) and 0. 
  - A SPR in the Range of 0.35-0.4 are ususaly considered a population at MSY level although this is a quite variable parameter. 
  - A population with SPR below 0.1-0.15 are considered collapsed.

## LBSPR Modes
LBSPR package contains functions to run the Length-Based Spawning Potential Ratio (LBSPR) method. The LBSPR package can be used in two ways: 

- **Simulating** the expected length composition, growth curve, and SPR and yield curves using the LBSPR model and 

- **Fitting** to empirical length data to provide an estimate of the spawning potential ratio (SPR).

## LBSPR data needed
The LBSPR method has been developed for data-limited fisheries, Data requested are: 

- A representative sample of the **size structure of the catch**.

- An understanding of the **life history** of the species. 

The LBSPR method does not require knowledge of the natural mortality rate (*M*), but instead uses the ratio of natural mortality and the von Bertalanffy growth coefficient (*K*) (*M*/*K*), which is believed to vary less across stocks and species than *M* (Prince et al. 2015).  

## LBSPR Assumptions
LBSPR model relies on a number of simplifying **assumptions**:

- The LBSPR models are equilibrium based.

- The length composition data is representative of the exploited population at steady state. Whith logistic selection.

See the publications listed in the reference list for full details of the assumptions of the model, including simulation testing to evauate the effect of violations of these assumptions.  

## SPR versions

### Age-Structured Length-Based Model
The LBSPR model described by Hordyk et al. (2015a, b), and tested in a MSE framework (Hordyk et al. 2015c), use a conventional age-structured equilibrium population model.  An important assumption of this model structure is that selectivity is age-based not length-based.

### Length-Structured Growth-Type-Group Model
Hordyk et al. (2016) describe a length-structured version of the LBSPR model that uses growth-type-groups (GTG) to account for size-based selectivity. The GTG-LBSPR model also has the ability to include variable *M* at size (by default *M* is assumed to be constant).  The GTG-LBSPR model typically estimates a lower fishing mortality rate for a given size structure compared to the earlier age-structured model.  This is because the age-structured model has a 'regeneration assumption', where, because of the age-based selectivity assumption, large individuals are expected even at high fishing mortality (large, young fish).

The default setting for the LBSPR package is to use the GTG-LBSPR model for all simulation and estimation. Control options in the simulation and estimation functions can be used to switch to the age-structured LBSPR model. 

Please make sure you understand the data and the biological parameters (and how the model treats these) and critically evaluate any output of the LBSPR model. 

## Installing and loading the Package

The LBSPR package is now available on CRAN:
```{r, eval=FALSE}
install.packages("LBSPR")
```
You can install the development version of the package from GitHub using the `devtools` package:
```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("AdrianHordyk/LBSPR")
```
Load the Package
```{r}
library(LBSPR)
```

# Fitting *Trisopteurs luscus* from Galician coast

```{r results='hide', message=FALSE, warning=FALSE}
library(tidyverse)
# date-time formats
library(lubridate)

# multipanel plots
# https://github.com/thomasp85/patchwork
# https://gotellilab.github.io/GotelliLabMeetingHacks/NickGotelli/ggplotPatchwork.html
# devtools::install_github("thomasp85/patchwork")
library(patchwork)

# some graphical fucntions are used
# install.packages("devtools")
# devtools::install_github("adrianhordyk/LBSPR")
library(LBSPR)
library(reshape2)

#tables
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
library(kableExtra)
library(knitr)
# http://haozhu233.github.io/kableExtra/use_kableExtra_with_formattable.html
library(formattable)
library(DT)

# info de las versiones 
sessionInfo()
```

We are going to use data of *Trisopterus luscus* from the observer monitoring programm of the **UTPB** (Xunta de Galicia). The data were recorded onboard small-scale fishing vessels working on shallow waters (up to 150 m depth) along the Galician coast since 1999. We choose data only from boats using **VETAS** fishing gear, as the most representative for this species (see Alonso-Fernández et al. 2019. 

*Trisopterus luscus* life history traits (LHT).

- MAturity oogive of females from Alonso-Fernandez et al. (2008), $L^{LIT}_{50} = 19.2 cm$, based on histology.

- Growth parameters (Von Bertalanffy) based on Labarta et al. (1982): $L^{LIT}_{inf} = 46.7 cm$;  $K^{LIT} = 0.21$; $t^{LIT}_{0} = 1.27$; $A^{LIT}_{max} = 9 years$.

- Estimates $M/K^{LIT}$ from Then et al. (2015). As reference we will usenatural moratlity estimates using growth parameters: $M_{VBGF} = 0.3699877 y^{-1}$; $M_{VBGF}/K^{LIT} = 1.761846$. But also we will try longevity: $M_{nls} = 0.6533320 y^{-1}$; $M_{nls}/K^{LIT} = 3.111105$. We used app [Barefoot Ecologist's Toolbox](http://barefootecologist.com.au/shiny_m).

**Tabla 1.** Parámetros del ciclo de vida de *Trisopterus luscus*. MLS = Minimun Landing Size (DOG), L50F = length maturity females, L50m = length maturity males, L50c = length maturity sex combined, Linf = asimptotic length von-bertalanfy.

```{r message=FALSE, warning=FALSE, echo=FALSE}
MyPars <- new("LB_pars")
slotNames(MyPars)

MyPars@Species <- "Trisopterus luscus"

# LHT
LHTs <- data.frame(t(c("Trisopterus luscus", 19.2, 1, 46.7, 0.21, 1.27, 9)))
colnames(LHTs) <- c("Sp", "L50", "Amat", "Linf", "K", "t0", "Amax")
natM <- read_delim("data\\M_tluscus.csv", delim = ",")
natM <- natM %>% 
  mutate(MK = M/0.21)
natM <- data.frame(natM[c(2, 8),])
LHTs$MKlit1 <- natM[1,4]
LHTs$MKlit2 <- natM[2,4]
LHTs$MK <- 1.5

# 95% probability mature
# Alonso-Fernánde et al. 2008: Pmat = a+bxTL
a <- -25.77
b <- 1.34
L95 <- (log(0.95/0.05)-a)/b

MyPars@Linf <- as.numeric(as.character(LHTs$Linf))
MyPars@L50  <- as.numeric(as.character(LHTs$L50 ))
MyPars@L95  <- L95
MyPars@MK   <- as.numeric(as.character(LHTs$MKlit2)) 
MyPars@SPR <- 0.4
MyPars@L_units <- "cm"
```

LB_lengths object read from *Trisopterus luscus* length frequency cvs file and plot.

```{r include=FALSE}
newDat <- read_csv("data\\faneca_size_9918.csv")
especie <- unique(newDat$SP)
arte <- unique(newDat$Gear)

newDat <- newDat %>% 
  select(TLength, Year)
newDat <- na.omit(newDat)
summary(newDat); dim(newDat)
newDat <- data.frame(do.call(cbind, unstack(newDat)))
colnames(newDat) <- seq(1999, 2018, 1)
dim(newDat)
summary(newDat)

write_csv(newDat, "data\\faneca.csv")
```

```{r }
MyLengths <- new("LB_lengths", LB_pars=MyPars, file="data\\faneca.csv", 
                 dataType="raw", header = TRUE)
```

## LB-SPR model

```{r, echo=FALSE, message=FALSE}
myFit <- LBSPRfit(MyPars, MyLengths)
```

Plotting length distribution fit. 

```{r}
plotSize(myFit)
```

Plotting yearly selectivity and maturity.

```{r}
plotMat(myFit)
```

Plotting yearly selectivity, F/M and SPR

```{r}
plotEsts(myFit)
```

**Tabla 2.** Summary table of LB-SRP model fit to *Trisopterus luscus* length data. 

```{r warning=FALSE}
LBSRP <- data.frame(
  Year    = seq(1999, 2018, 1),
  SL50 = myFit@SL50,
  SL95 = myFit@SL95,
  FM   = myFit@FM,
  SPR  = myFit@SPR
  )

LBSRP <- LBSRP %>% 
  mutate_if(is.numeric, round, 2)

LBSRP %>%
  mutate(
    FM = color_tile("white", "red")(FM),
    SPR = ifelse(
      SPR > 0.4,
      cell_spec(SPR,
                background  = "green", bold = T, color = "white", align = "center"),
      ifelse(SPR > 0.1,
             cell_spec(SPR, 
                       background  = "orange", italic = T, color = "white", align = "center" ),
             cell_spec(SPR,
                       background  = "red", italic = T, color = "white", align = "center")))
    ) %>%
  kable(escape = F) %>%
  kable_styling("striped", full_width = F) %>%
  column_spec(5, width = "3cm") 
``` 

## Sensitivity analysis

We change values of $L_{inf}$ and $M/K$ to evaluate effect os LBSPR results.

```{r include=FALSE}
# M/K = 0.75 x M/K(LIT)
MyParsMKLow <- MyPars
MyParsMKLow@MK <- 0.75*MyPars@MK
MyLengthsMKLow <- new("LB_lengths", LB_pars=MyParsMKLow, file="data\\faneca.csv", 
                 dataType="raw", header = TRUE)
MyLengthsMKLow@L_units <- MyParsMKLow@L_units
myFitMKLow <- LBSPRfit(MyParsMKLow, MyLengthsMKLow)

# M/K = 1.25 x M/K(LIT)
MyParsMKSup <- MyPars
MyParsMKSup@MK <- 1.25*MyPars@MK
MyLengthsMKSup <- new("LB_lengths", LB_pars=MyParsMKSup, file="data\\faneca.csv", 
                     dataType="raw", header = TRUE)
MyLengthsMKSup@L_units <- MyParsMKSup@L_units
myFitMKSup <- LBSPRfit(MyParsMKSup, MyLengthsMKSup)

# M/K = 1.5
MyParsMK15 <- MyPars
MyParsMK15@MK <- 1.5
MyLengthsMK15 <- new("LB_lengths", LB_pars=MyParsMK15, file="data\\faneca.csv", 
                     dataType="raw", header = TRUE)
MyLengthsMK15@L_units <- MyParsMK15@L_units
myFitMK15 <- LBSPRfit(MyParsMK15, MyLengthsMK15)

# M/K = 3.1 (mortality based on longecity; Then et al. 2015)
MyParsMKnls <- MyPars
MyParsMKnls@MK <- 3.111105
MyLengthsMKnls <- new("LB_lengths", LB_pars=MyParsMKnls, file="data\\faneca.csv", 
                     dataType="raw", header = TRUE)
MyLengthsMKnls@L_units <- MyParsMKnls@L_units
myFitMKnls <- LBSPRfit(MyParsMKnls, MyLengthsMKnls)

# Linf = 0.75 x Linf(LIT)
MyParsLinfLow <- MyPars
MyParsLinfLow@Linf <- 0.75*MyPars@Linf
MyLengthsLinfLow <- new("LB_lengths", LB_pars=MyParsLinfLow, file="data\\faneca.csv", 
                      dataType="raw", header = TRUE)
MyLengthsLinfLow@L_units <- MyParsLinfLow@L_units
myFitLinfLow <- LBSPRfit(MyParsLinfLow, MyLengthsLinfLow)

# Linf = 1.25 x Linf(LIT)
MyParsLinfSup <- MyPars
MyParsLinfSup@Linf <- 1.25*MyPars@Linf
MyLengthsLinfSup <- new("LB_lengths", LB_pars=MyParsLinfSup, file="data\\faneca.csv", 
                      dataType="raw", header = TRUE)
MyLengthsLinfSup@L_units <- MyParsLinfSup@L_units
myFitLinfSup <- LBSPRfit(MyParsLinfSup, MyLengthsLinfSup)

myFitEsts         <- data.frame(myFit@Ests)
myFitMKLowEsts    <- data.frame(myFitMKLow@Ests)
myFitMKSupEsts    <- data.frame(myFitMKSup@Ests)
myFitMK15Ests     <- data.frame(myFitMK15@Ests)
myFitMKnlsEsts    <- data.frame(myFitMKnls@Ests)
myFitLinfLowEsts <- data.frame(myFitLinfLow@Ests)
myFitLinfSupEsts  <- data.frame(myFitLinfSup@Ests)


sprRef     = myFit@SPR
sprMKLow   = myFitMKLow@SPR
sprMKSup   = myFitMKSup@SPR
sprMK15    = myFitMK15@SPR
sprMKnls   = myFitMKnls@SPR
sprLinfLow = myFitLinfLow@SPR
sprLinfSup = myFitLinfSup@SPR

sprRef2     = myFit@FM
sprMKLow2   = myFitMKLow@FM
sprMKSup2   = myFitMKSup@FM
sprMK152    = myFitMK15@FM
sprMKnls2   = myFitMKnls@FM
sprLinfLow2 = myFitLinfLow@FM
sprLinfSup2 = myFitLinfSup@FM
```

```{r  Figure1, cache= TRUE, fig.cap="Figure 1. SPR estimates for each of the scenarios of the sensitivity analysis.", fig.align = "center", dpi=200, fig.height = 7, fig.width = 9}
colors <-
  c(
    "Reference" = "black",
    "0.75xMK"   = "red",
    "1.25xMK"   = "green",
    "MK=1.5"    = "grey",
    "MK=3.1"    = "yellow",
    "0.75xLinf" = "orange",
    "1.25xLinf" = "blue"
  )

Year <- seq(1999, 2018, 1)

p_SPR <- ggplot() +
  geom_hline(yintercept = 0.4,
             col = "black",
             linetype = "dotted", size = 1.25) +
  geom_line(aes(x = Year, y = myFitEsts$SPR, color = "Reference")) +
  geom_point(aes(x = Year, y = sprRef), col = "white", size = 3.5) +
  geom_point(aes(x = Year, y = sprRef, color = "Reference"),  size = 3, alpha = 0.5) +
  geom_line(aes(x = Year, y = myFitMKLowEsts$SPR, color = "0.75xMK")) +
  geom_point(aes(x = Year, y = sprMKLow), col = "white", size = 3.5) +
  geom_point(aes(x = Year, y = sprMKLow, color = "0.75xMK"),  size = 3, alpha = 0.5) +
  geom_line(aes(x = Year, y = myFitMKSupEsts$SPR, color = "1.25xMK")) +
  geom_point(aes(x = Year, y = sprMKSup), col = "white", size = 3.5) +
  geom_point(aes(x = Year, y = sprMKSup, color = "1.25xMK"),  size = 3, alpha = 0.5) +
  geom_line(aes(x = Year, y = myFitMK15Ests$SPR, color = "MK=1.5")) +
  geom_point(aes(x = Year, y = sprMK15), col = "white", size = 3.5) +
  geom_point(aes(x = Year, y = sprMK15, color = "MK=1.5"),  size = 3, alpha = 0.5) +
  geom_line(aes(x = Year, y = myFitMKnlsEsts$SPR, color = "MK=3.1")) +
  geom_point(aes(x = Year, y = sprMKnls), col = "white", size = 3.5) +
  geom_point(aes(x = Year, y = sprMKnls, color = "MK=3.1"),  size = 3, alpha = 0.5) +
  geom_line(aes(x = Year, y = myFitLinfLowEsts$SPR, color = "0.75xLinf")) +
  geom_point(aes(x = Year, y = sprLinfLow), col = "white", size = 3.5) +
  geom_point(aes(x = Year, y = sprLinfLow, color = "0.75xLinf"),  size = 3, alpha = 0.5) +
  geom_line(aes(x = Year, y = myFitLinfSupEsts$SPR, color = "1.25xLinf")) +
  geom_point(aes(x = Year, y = sprLinfSup), col = "white", size = 3.5) +
  geom_point(aes(x = Year, y = sprLinfSup, color = "1.25xLinf"),  size = 3, alpha = 0.5) +
  labs(x = "Year",
       y = "SPR",
       color = " ") +
  scale_color_manual(values = colors) + 
  theme_bw()

p_SPR
```

```{r  Figure2, cache= TRUE, fig.cap="Figure 2. F/M estimates for each of the scenarios of the sensitivity analysis.", fig.align = "center", dpi=200, fig.height = 7, fig.width = 9}
p_FM <- ggplot() +
  geom_hline(yintercept = 1,
             col = "black",
             linetype = "dotted", size = 1.25) +
  geom_line(aes(x = Year, y = myFitEsts$FM, color = "Reference")) +
  geom_point(aes(x = Year, y = sprRef2), col = "white", size = 3.5) +
  geom_point(aes(x = Year, y = sprRef2, color = "Reference"),  size = 3, alpha = 0.5) +
  geom_line(aes(x = Year, y = myFitMKLowEsts$FM, color = "0.75xMK")) +
  geom_point(aes(x = Year, y = sprMKLow2), col = "white", size = 3.5) +
  geom_point(aes(x = Year, y = sprMKLow2, color = "0.75xMK"),  size = 3, alpha = 0.5) +
  geom_line(aes(x = Year, y = myFitMKSupEsts$FM, color = "1.25xMK")) +
  geom_point(aes(x = Year, y = sprMKSup2), col = "white", size = 3.5) +
  geom_point(aes(x = Year, y = sprMKSup2, color = "1.25xMK"),  size = 3, alpha = 0.5) +
  geom_line(aes(x = Year, y = myFitMK15Ests$FM, color = "MK=1.5")) +
  geom_point(aes(x = Year, y = sprMK152), col = "white", size = 3.5) +
  geom_point(aes(x = Year, y = sprMK152, color = "MK=1.5"),  size = 3, alpha = 0.5) +
  geom_line(aes(x = Year, y = myFitMKnlsEsts$FM, color = "MK=3.1")) +
  geom_point(aes(x = Year, y = sprMKnls2), col = "white", size = 3.5) +
  geom_point(aes(x = Year, y = sprMKnls2, color = "MK=3.1"),  size = 3, alpha = 0.5) +
  geom_line(aes(x = Year, y = myFitLinfLowEsts$FM, color = "0.75xLinf")) +
  geom_point(aes(x = Year, y = sprLinfLow2), col = "white", size = 3.5) +
  geom_point(aes(x = Year, y = sprLinfLow2, color = "0.75xLinf"),  size = 3, alpha = 0.5) +
  geom_line(aes(x = Year, y = myFitLinfSupEsts$FM, color = "1.25xLinf")) +
  geom_point(aes(x = Year, y = sprLinfSup2), col = "white", size = 3.5) +
  geom_point(aes(x = Year, y = sprLinfSup2, color = "1.25xLinf"),  size = 3, alpha = 0.5) +
  labs(x = "Year",
       y = "F/M",
       color = " ") +
  scale_color_manual(values = colors) + 
  theme_bw()

p_FM
```

# Conclusions

- Reasonably good fit of length distributions. 

- We do not have any reference of selectivity parameters to compare. In any case it is reaseanoble to think that a gillnet, like **VETAS**, has a **dome-shape selectivity curve**, which soes not agree with current model asumptions. Hommik et al. (2020) updated the LB-SRP method to fit dome-shaped selectivity (normal and log-normal). User has to pre-specify selectivity parameters derived from select_Millar function of *TropFishR* package  (Taylorand and Mildenberger 2017). However it is required to conduct experimental catcheswith different mesh sizes to get selectivity patterns, and to date we do not have such info.  

- F/M ratio quite high (average value along time series of 3.4). 

- SPR low (average value along time series of 0.14) when optimum is between 0.35-0.4; but above collapsed threshold of 0.1.

- Further considerations: i) It is uncertain the effect of a likely dome-shape selectivity curve. That would probably affect estimates of **SPR (underestimate?)** and **F/M (overestimate?**); ii) although not teste here, it is known that Linf is a very sensitive parameter in this kind of models, so, proper estimates of growth parameters is required; iii) current methodology used to estimate proportion of matures (we consider mature base on presence of secondary follicles in the ovary) does not necesarilly means proportion of active spawning females (Prince, personal communication at LBSPR course in Vigo, 2019), so, changing consideration of proportion of spawning females could provide different SPR estimates.

- Regarding the sensitivity analysis, $L_{inf}$ is a parameter with huge influence of SPR, lower values of $L_{inf}$ results in better pereception of stock status.

# References

- Alonso-Fernández, A.; Domínguez-Petit, R.; Bao, M.; Rivas, C.; Saborido-Rey, F., 2008. Spawning pattern and reproductive strategy of female pouting Trisopterus luscus (Gadidae) on the Galician shelf of north-western Spain. Aquat Living Resour. 21, 383-393

- Alonso-Fernández, A.; Otero, J.; Bañón, R.; Campelos, J.M.; Quintero, F.; Ribó, J.; Filgueira, F.; Juncal, L.; Lamas, F.; Gancedo, A.; Molares, J., 2019. Inferring abundance trends of key species from a highly developed small-scale fishery off NE Atlantic. Fish Res. 209, 101-116

- Hommik, K.; Fitzgerald, C.J.; Kelly, F.; Shephard, S., 2020. Dome-shaped selectivity in LB-SPR: Length-Based assessment of data-limited inland fish stocks sampled with gillnets. Fish Res. 229, 105574

- Hordyk, A.R., Ono, K., Sainsbury, K.J., Loneragan, N., and Prince, J.D. 2015a. Some explorations of the life history ratios to describe length composition, spawning-per-recruit, and the spawning potential ratio. ICES J. Mar. Sci. 72: 204 - 216.

- Hordyk, A.R., Ono, K., Valencia, S.R., Loneragan, N.R., and Prince, J.D. 2015b. A novel length-based empirical estimation method of spawning potential ratio (SPR), and tests of its performance, for small-scale, data-poor fisheries. ICES J. Mar. Sci. 72: 217 – 231. 

- Hordyk, A.R., Loneragan, N.R., and Prince, J.D. 2015c. An evaluation of an iterative harvest strategy for data-poor fisheries using the length-based spawning potential ratio assessment methodology. Fish. Res. 171: 20– 32.

- Hordyk, A., Ono, K., Prince, J.D., and Walters, C.J. 2016. A simple length-structured model based on life history ratios and incorporating size-dependent selectivity: application to spawning potential ratios for data-poor stocks. Can. J. Fish. Aquat. Sci. 13: 1– 13. doi: 10.1139/cjfas-2015-0422.

- Labarta, U.; Ferreiro, M.J.; Fenandez, M.T.; Martinez, F., 1982 Spawning season and first maturity size and age of the Galician coast pouting (Trisopterus luscus L.). Council Meeting, 1982a, of the International Council for the Exploration of the Sea, (Copenhagen (Denmark)), (11 Oct 1982). COPENHAGEN (DENMARK): ICES

- Labarta, U.; Ferreiro, M.J.; Martinez, F.; Fernandez, M.T., 1982 Age and growth of the Galician coast pouting (Trisopterus luscus L.). Preliminary data. Council Meeting, 1982, of the International Council for the Exploration of the Sea, (Copenhagen (Denmark)), (11 Oct 1982). COPENHAGEN (DENMARK): ICES

- Prince, J.D., Hordyk, A.R., Valencia, S.R., Loneragan, N.R., and Sainsbury, K.J. 2015. Revisiting the concept of Beverton–Holt life-history invariants with the aim of informing data-poor fisheries assessment. ICES J. Mar. Sci. 72: 194 - 203.

- Taylor M.H., Mildenberger T.K. (2017). Extending electronic length frequency analysis in R. Fisheries Management and Ecology, 24(4): 230-238. ISSN 0969997X, doi: 10.1111/fme.12232 (https://doi.org/10.1111/fme.12232)

# Web resources

https://raw.githubusercontent.com/ices-tools-dev/ICES_MSY/master/R/LBSPR.R

https://raw.githubusercontent.com/ices-tools-dev/ICES_MSY/master/R/LBI.R

https://github.com/AdrianHordyk/LBSPR

https://github.com/merrillrudd/LIME/wiki

http://barefootecologist.com.au/

https://github.com/KHommik/DomeShaped_GTG_LBSPR
